Smoothing seismicity techniques applied to seismic sources characterization and probabilistic seismic hazard analysis in Brazil

### 2014-10-07 manuscript.tex
abstract

abrastcasrtasdlkjh alksjd flkajhsd flkjahds flkjahsdlkfja slkdjfh alskjdfh laksjdhf lakjshdfl ajhds lfkja lksdjflaksjdf
lakjsf akjshdfl akjdsfljkahds lfkjahds lkjahsdlfkjas ldkjfh laskjdhf laksjf lasdfh
asdflkajf lkajshdf lajshdfliuhp 9qerjhtgnv.k, zmxcnpq;awe. ksmdnf va.,fxcnvpq ;.jars,mndf vq;asgdv
qolehfbd nvqlas,dbnv qalsd.vjhbq oalsk.ezjrbnfc;wq asdl.Zxgjyvqehratnpg oq;ve.krasj gbeq;adr.fxngb

>>>>

Intraplate seismicity is a hard problem to solve in tectonics, main during the lack of observed seismicity in
many areas where seismic hazard assesment are also difficult and the methods applied
are often close correlated to the geometries defined by the experts, of course, with valuable criteria.

Three smoothing seismicity techniques are reviewed in order to investigate their appliability to the 
Brazilian seismicity and seismic hazard assesment case. 
All these methods are \emph{catalog-based} in contrast to standard zoning \emph{expert-based} methods from Cornell and
McGuire. Of course it does not mean that the expert there is no value and many parameters needs to be configured.

All the methods are based on a kernel density estimation, but the main diffence between them is the
\emph{bandwidth selection} process. The Frankel method use a \emph{fixed} bandwidth in space, Woo method is based on
\emph{magnitude} also and the Helmstetter is a \emph{local-adaptive} in space and time bandwidth selection. This last
mathod was proposed originally to care the background seismicity rate on long-term earthquake forecast but the one year
forecast is exactly the annual seismic rate used to define a seismic source under a time-independent assumption.

In the conclusions the results shown that all methods gives good results and could be used in the Brazilian
seismicity case, all of them, improoving the spatial resolution of the actual state-of-art GSHAP model. 
The Last two methods was implemented and are available as a free software on HMTK from GEM Foundation. All the hazard
calculations was performed on OpenQuake open source software.
